---
title: "Assignment 1"
---

# Assignment 1

```{r}
1 + 1
```

My first assignment has two parts.

## (a)

## Selected Video

Video Title: Veri Bilimi ve Endüstri Mühendisliği Üzerine Sohbetler- Mustafa Baydoğan & Erdi Daşdemir

### Summary

Mustafa Hoca, a faculty member in Industrial Engineering at Boğaziçi University and an entrepreneur working on data science and optimization projects, emphasized the importance of applied learning in data analysis, machine learning, and optimization. Through real-world examples such as inventory management, retail sales forecasting, and balancing electricity production and consumption, he demonstrated how data collection, preprocessing, feature extraction, prediction, and decision-making processes are applied in practice. He also discussed the advantages of traditional machine learning and deep learning methods, as well as topics such as explainable artificial intelligence and reinforcement learning. His advice to students was to combine theory with practice by working on real-world problems, consider focusing on data science and optimization in their graduate studies, and gain hands-on experience through mentorship and project-based environments.

### Open-ended Question

**Question:** How would you connect the steps of data collection, feature extraction, prediction, and optimization?

**Answer:** First, I collect and clean the data. Then, I extract the important features from the data and use prediction models to estimate future outcomes. Finally, I integrate these predictions into optimization models to determine the best decision.

### Multiple Choice Question

**Question:** Which method is used to explain the reasons behind models when making decisions?

A\) Deep Learning\
B) Reinforcement Learning\
C) Data Visualization\
D) Explainable Artificial Intelligence

**Answer:** D) Explainable Artificial Intelligence

## (b)

```{r}

library(dslabs)
data("polls_us_election_2016")

my_first <- "Aysenaz"
my_birth_year <- 2004
k <- (nchar(my_first) + my_birth_year) %% 15 + 8

if (k %% 2 == 0) {
  head(polls_us_election_2016, k)
} else {
  tail(polls_us_election_2016, k)
}

total_na <- sum(is.na(polls_us_election_2016))
column_na <- sort(colSums(is.na(polls_us_election_2016)), decreasing = TRUE)
print(total_na)
print(head(column_na, 8))

new_data <- polls_us_election_2016
for (col in names(new_data)) {
  if (is.numeric(new_data[[col]])) {
    new_data[[col]][is.na(new_data[[col]])] <- my_birth_year + k
  } else if (is.character(new_data[[col]]) || is.factor(new_data[[col]])) {
    new_data[[col]] <- as.character(new_data[[col]])
    new_data[[col]][is.na(new_data[[col]])] <- paste0(my_first, "_", k)
  }
}

if (k %% 2 == 0) {
  head(new_data, k)
} else {
  tail(new_data, k)
}

knitr::kable(tail(polls_us_election_2016, k))

print(sum(is.na(new_data)))
print(anyNA(new_data))


```
